Forcasting US Elections using Polls-of-Polls

### 2024-10-22 paper/paper.qmd
Made some changes.

---
title: Forcasting US Elections using Polls-of-Polls
subtitle: "My subtitle if needed"
author: 
  - Shamayla Durrin
  - Denise Chang 
  - Krishna Kumar
thanks: "Code and data are available at: [https://github.com/krishnak30/US_elections](https://github.com/krishnak30/US_elections)."

date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
library(psych)
library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
library(kableExtra)
library(sf)
library(tidyverse)
library(plotly)
library(RColorBrewer)
library(stringr)
library(modelsummary)
library(broom)
library(sf)
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
mapping_data <- st_read(here("data/03-shapefiles_data/US"))
mean_support_data <- read_parquet(here("data/02-analysis_data/mapping_data.parquet"))
```

@@

@@

### Summary of Variables of Interest

```{r}
# Assuming you have the dataset numeric_data already loaded
#| include: false
#| warning: false
#| message: false

numeric_data <- analysis_data %>% select(numeric_grade, pollscore, sample_size, pct, num_support)

# Create a summary table
summary_table <- numeric_data %>%
  reframe(
    `Variable` = c("numeric_grade", "pollscore", "sample_size", "pct", "num_support"),
    `Mean` = c(mean(numeric_grade, na.rm = TRUE), 
               mean(pollscore, na.rm = TRUE), 
               mean(sample_size, na.rm = TRUE), 
               mean(pct, na.rm = TRUE), 
               mean(num_support, na.rm = TRUE)),
    `Max` = c(max(numeric_grade, na.rm = TRUE), 
              max(pollscore, na.rm = TRUE), 
              max(sample_size, na.rm = TRUE), 
              max(pct, na.rm = TRUE), 
              max(num_support, na.rm = TRUE)),
    `Min` = c(min(numeric_grade, na.rm = TRUE), 
              min(pollscore, na.rm = TRUE), 
              min(sample_size, na.rm = TRUE), 
              min(pct, na.rm = TRUE), 
              min(num_support, na.rm = TRUE)),
    `Standard Deviation` = c(sd(numeric_grade, na.rm = TRUE), 
                             sd(pollscore, na.rm = TRUE), 
                             sd(sample_size, na.rm = TRUE), 
                             sd(pct, na.rm = TRUE), 
                             sd(num_support, na.rm = TRUE))
  )

kable(summary_table)
```

## Variables

The data set contains a wide range of variables that are essential for understanding polling outcomes. The following are key variables:

-   **`poll_id`**: Unique identifier for each poll conducted.

-   **`pollster`**: The polling organization that conducted the poll (e.g., YouGov, TIPP).

-   **`numeric_grade`**: A numeric rating indicating the pollster’s quality or reliability (e.g., 1.8).

-   **`pollscore`**: A score representing the reliability of the pollster in terms of error and bias.

-   **`state`**: The state where the poll was conducted (or "Not Applicable" for national polls).

-   **`start_date` / `end_date`**: Dates during which the poll was conducted.

-   **`sample_size`**: The number of respondents in the poll.

-   **`population`**: The group surveyed (e.g., likely voters or registered voters).

-   **`candidate_name`**: The name of the candidate being polled (e.g., Kamala Harris, Donald Trump).

-   **`pct`**: The percentage of support for the candidate in the poll.

-   **`methodology`**: The method used to conduct the poll (e.g. online panel)

-   **`transparency_score`**: A grade for how transparent a pollster is, calculated based on how much information it discloses about its polls and weighted by recency. The highest Transparency Score is 10.

## Summary Statistics

### 1) Average Pollster Quality (pollscore): mean, median, mode, min, max

```{r}
library(dplyr)

# Generate summary statistics for national and state polls
summary_stats <- analysis_data %>%
  filter(!is.na(pollscore)) %>%  # Exclude rows with missing pollscore
  group_by(national) %>%        # Group by poll_scope
  summarize(
    Count = n(),                   
    Min = round(min(pollscore), 2),
    `1st Qu.` = round(quantile(pollscore, 0.25), 2),
    Median = round(median(pollscore), 2),
    Mean = round(mean(pollscore), 2),
    `3rd Qu.` = round(quantile(pollscore, 0.75), 2),
    Max = round(max(pollscore), 2),
    .groups = 'drop'  # Drop grouping structure for cleaner output
  )

# Print the summary statistics
kable(summary_stats)

@@

As shown above, the summary statistics table **\[CROSS-REFERENCE HERE\]** offers an overview of poll scores for national and state polls, with 2,971 and 2,953 entries, respectively. Both categories feature a minimum poll score of -1.5, which a high level of validity and reliability. The first quartile shows national polls at -0.9, while state polls are slightly lower at -1.1. Median scores are -0.3 for national polls and -0.4 for state polls, suggesting that half of the polls in both categories yield moderately negative scores, reinforcing a trend of favorable sentiment. The mean score is -0.37 for national polls, indicating a less reliable perception compared to the -0.51 mean for state polls. The third quartile for national polls (0.0) indicates that the upper 25% of scores are neutral, while state polls remain just below neutral at 0.7. The maximum score of 1.7 for national polls reflects a notable negative perception for at least one candidate, while the maximum for state polls is 0.7. Overall, these statistics illustrate a strong reliability of pollsters considering their errors and bias.

```         
```

### 2) Distribution of sample sizes: same as above

```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)  # Load the gridExtra package

# Create a new variable for sample size ranges
analysis_data <- analysis_data %>%
  mutate(sample_size_range = case_when(
    sample_size <= 10000 ~ "0-10,000",
    sample_size > 10000 & sample_size <= 20000 ~ "10,001-20,000",
    sample_size > 20000 & sample_size <= 30000 ~ "20,001-30,000",
    TRUE ~ "Above 30,000"
  ))

# Plot for 0-10,000
p1 <- ggplot(analysis_data %>% filter(sample_size <= 10000), aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "lightgreen", color = NA, alpha = 0.7) +
  labs(title = "Sample Sizes 
       (0-10,000)",
       x = "Sample Size",
       y = "Count") +
  scale_x_continuous(limits = c(0, 10000)) +  # Set x limits for the first plot
  scale_y_continuous(limits = c(0, 2300)) +  # Set y limits for the first plot
  theme_minimal() +
  theme(plot.title = element_text(size = 10),  # **Decreased font size of the title**
        axis.title.y = element_text(margin = margin(r = 15)))  # **Increased gap for y-axis label**

# Plot for 10,001 - 20,000
p2 <- ggplot(analysis_data %>% filter(sample_size > 10000 & sample_size <= 20000), aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "indianred", color = NA, alpha = 0.7) +
  labs(title = "Sample Sizes 
       (10,001-20,000)",
       x = "Sample Size",
       y = "Count") +
  scale_x_continuous(limits = c(10001, 20000)) +  # Set x limits for the second plot
  scale_y_continuous(limits = c(0, 50)) +  # Set y limits for the second plot
  theme_minimal() +
  theme(plot.title = element_text(size = 10),  # **Decreased font size of the title**
        axis.title.y = element_text(margin = margin(r = 10)))  # **Increased gap for y-axis label**

# Plot for 20,001 - 30,000
p3 <- ggplot(analysis_data %>% filter(sample_size > 20000 & sample_size <= 30000), aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "lightblue", color = NA, alpha = 0.7) +
  labs(title = "Sample Sizes 
       (20,001-30,000)",
       x = "Sample Size",
       y = "Count") +
  scale_x_continuous(limits = c(20001, 30000)) +  # Set x limits for the third plot
  scale_y_continuous(limits = c(0, 10)) +  # Set y limits for the third plot
  theme_minimal() +
  theme(plot.title = element_text(size = 10),  # **Decreased font size of the title**
        axis.title.y = element_text(margin = margin(r = 5)))  # **Increased gap for y-axis label**

# Arrange the plots side by side
grid.arrange(p1, p2, p3, ncol = 3)  # ncol=3 arranges the plots in one row

@@

The histograms **\[CROSS-REFERENCE HERE\]** reveal significant trends in sample sizes across the different ranges, indicating a general tendency towards smaller samples in the polling data. Most values within the 0-10,000 range cluster at the lower end, suggesting that many polls are conducted with limited respondent numbers, which may compromise the reliability and representativeness of the results. **However, this conclusion is very much dependent on what we determine to be an acceptable sample size for the results to be considered reliable**. In the 10,001-20,000 range, while there is some increase in sample sizes, the majority still falls within the 10,000-12,500 bracket, with few reaching the upper limits.

The findings from the 20,001-30,000 range further illustrate the scarcity of larger sample sizes, with only a couple of values noted at each of the significant points. This distribution emphasizes a preference for smaller samples in the polling data analyzed.

In the context of polling results, these findings suggest potential limitations in the accuracy and validity of the insights generated. Larger sample sizes are typically preferred in polling as they tend to yield more reliable estimates and reduce the margin of error, leading to a better representation of the population's views. Consequently, the predominance of smaller sample sizes in this data set may raise concerns about the robustness of the polling findings, potentially affecting their applicability in broader analyses or decision-making processes. However, we must determine an acceptable and ideal sample size that would allow us to determine the reliability of these results.

# Forecasting Approach Using Polls of Polls Method

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-enddate
#| fig-cap: "Support for Kamala Harris based on End Date and colored by Pollster's Error and Bias."

@@

```{r}
# Filter out non-continental states (Hawaii and Alaska)
us_states_filtered <- mapping_data %>% 
  filter(!NAME %in% c("Alaska", "Hawaii"))

@@

# Plot using geom_sf() for sf objects
p <- ggplot(map_data_full) +
  geom_sf(aes(fill = mean_support_kamala, text = paste("State:", str_to_title(NAME), "<br>Average Support:", round(mean_support_kamala, 2))), color = "white") +  # Capitalize state names
  scale_fill_distiller(palette = "RdBu", direction = 1, na.value = "gray", name = "Kamala's Support") +  # Reverse RdBu color gradient
  geom_text(data = state_centroids, aes(geometry = geometry, label = STUSPS), stat = "sf_coordinates", size = 2) +  # State labels
  labs(title = "Support for Kamala Harris by State", 
       caption = "States with no polling data are shown in gray") +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5),
    panel.grid = element_blank(),  # Remove grid lines
    axis.title = element_blank(),  # No axis titles for maps
    axis.text = element_blank(),   # No axis labels
    axis.ticks = element_blank()   # No axis ticks
  )

@@

$$ y_i = \alpha + \beta_1 \cdot \texttt{pollster}_i + \beta_2 \cdot \texttt{sample_size}_i + \beta_3 \cdot \texttt{recency}_i +  \beta_4 \cdot \texttt{state}_i + \epsilon_i $$

@@

```{r}
# Load necessary libraries
library(broom)
library(dplyr)
library(knitr)

# Load the models from RDS files
model_1 <- readRDS(here("models/model_1.rds"))
model_2 <- readRDS(here("models/model_2.rds"))
model_3 <- readRDS(here("models/model_3.rds"))

@@

```{r}
# Create a data frame for AIC and BIC comparison
aic_bic_table <- data.frame(
  Model = c("Model 1", "Model 2", "Model 3"),
  AIC = c(AIC(model_1), AIC(model_2), AIC(model_3)),
  BIC = c(BIC(model_1), BIC(model_2), BIC(model_3))
)

@@

@@

# Load necessary libraries
library(modelsummary)
library(broom)

# Load Model 3 from RDS file
model_3 <- readRDS(file = here::here("models/model_3.rds"))

# Generate LaTeX output for the model
latex_output <- modelsummary(model_3, output = "latex")

# Ensure the output is a character string
latex_output_string <- capture.output(cat(latex_output))

# Write the LaTeX string to a .tex file
writeLines(latex_output_string, here::here("model_3_summary.tex"))

@@

```{r}
# Save LaTeX output to a string
latex_output <- modelsummary(model_3, output = "latex")

# Write the LaTeX string to a .tex file
writeLines(latex_output, here::here("output/model_3_summary.tex"))
```

# Load necessary libraries
library(modelsummary)
library(broom)

# Load Model 3 from RDS file
model_3 <- readRDS(file = here::here("models/model_3.rds"))

modelsummary(model_3, output = "latex", file = "model_3_summary.tex")
```

# Load necessary libraries
library(modelsummary)
library(broom)

# Load Model 3 from RDS file
model_3 <- readRDS(file = here::here("models/model_3.rds"))

modelsummary(model_3)

# Display the summary of Model 3 using modelsummary
#| echo: false
#| eval: true
#| label: tbl-model3results
#| tbl-cap: "Regression results for Model 3 including Pollster, Sample Size, State, and Recency"

modelsummary::modelsummary(
  list(
    "Model 3" = model_3
  ),
  statistic = "std.error",
  fmt = 2
)

Our results are summarized in @tbl-modelresults.

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: Forcasting US Elections using Polls-of-Polls
subtitle: "My subtitle if needed"
author: 
  - Shamayla Durrin
  - Denise Chang 
  - Krishna Kumar
thanks: "Code and data are available at: [https://github.com/krishnak30/US_elections](https://github.com/krishnak30/US_elections)."
date: today
date-format: long
abstract: "This paper uses a polls of polls approach to predict voter support for Kamala Harris in the 2024 U.S. election, aggregating multiple polls to reduce individual bias and improve accuracy. Through a regression model incorporating factors such as pollster, sample size, state, and recency, we predict her overall support to be 47.78%, just below the 50% threshold. Our analysis highlights the importance of poll quality and recency in understanding trends in public opinion. These findings are significant as they provide a more reliable estimate of electoral outcomes, helping to inform political strategies and public discourse."
format: html
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(psych)
library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
library(kableExtra)
library(sf)
library(tidyverse)
library(plotly)
library(RColorBrewer)
library(stringr)
library(modelsummary)
library(broom)
library(sf)
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
mapping_data <- st_read(here("data/03-mapping_data/US"))
mean_support_data <- read_parquet(here("data/02-analysis_data/map_data.parquet"))
```

@@

While individual polls provide snapshots of public opinion, they are often subject to biases and methodological differences. To address these limitations, this paper uses a "polls of polls" approach to predict support for Kamala Harris, aggregating multiple polls to smooth out inconsistencies. By combining data from various polling organizations, our aim is to create a more accurate forecast of her voter support leading up to the 2024 U.S. election.

We employ a linear regression model to estimate Kamala Harris' support percentage, incorporating key variables such as pollster, sample size, state, and recency. To account for the varying reliability of different polls, we weight predictions using each pollster’s numeric grade. Our model also explores the role of recency, with recent polls showing a decline in support for Harris. The final weighted prediction for her support stands at 47.78%, indicating that her overall backing falls just below the 50% threshold, suggesting potential challenges in gaining majority support.

This paper contributes to the field of election forecasting by emphasizing the importance of poll quality and recency in prediction models. The structure of the paper proceeds as follows: we first introduce the dataset and methodology, followed by model selection and results. We then discuss the implications of our findings, and conclude with limitations and potential directions for future research.

@@

### Summary Statistics of Variables of Interest

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

library(dplyr)
library(modelsummary)
library(tools)  
library(kableExtra)

# Set options to use kableExtra for table formatting
options(modelsummary_factory_default = 'kableExtra')

# Create the summary statistics table for the specified numerical variables
summary_table <- analysis_data %>%
  select(numeric_grade, pollscore, sample_size, num_support) %>%
  # Remove underscores and capitalize the first letter of each word
  rename_with(~ toTitleCase(gsub("_", " ", .))) %>%
  datasummary_skim(
    fun_numeric = list(
      Mean = mean,
      SD = sd,
      Min. = min,
      Median = median,
      Max. = max
    )
  )

print(summary_table)

#(summary_table)

#kable(summary_table, caption = "Summary of Variables of Interest") %>% kable_styling(full_width = FALSE)

@@

The summary statistics table presents key descriptive measures for the numeric variables of interest. The Numeric Grade variable has a mean of 2.3, with values ranging from a minimum of 1.1 to a maximum of 3.0. It has a standard deviation of 0.6, indicating relatively low variability. The Pollscore variable averages -0.5, with a standard deviation of 0.6 and a range between -1.5 and 1.7. The Sample Size has a wider range, with an average of 1962.5 and a standard deviation of 2608.0, indicating significant variation across polls, with values spanning from 382 to 12084. Lastly, Num Support, calculated as the number of respondents supporting Kamala Harris, shows a mean of 949.2, with values ranging from 172 to 6042 and a standard deviation of 1290.0, highlighting substantial differences across the polls.

### Distribution of Sample Size of Polls

```{r}
#| warning: false
#| message: false
#| echo: false

library(ggplot2)

# Plot histogram for all sample sizes
ggplot(analysis_data, aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "lightblue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Sample Sizes",
       x = "Sample Size",
       y = "Count") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove grid lines
    plot.title = element_text(size = 14, hjust = 0.5),  # Center the title
    axis.title.y = element_text(margin = margin(r = 10))  # Increased gap for y-axis label
  )

@@

The histogram of sample sizes reveals a clear right-skewed distribution. Most of the sample sizes are clustered between 0 and 3000, with a sharp peak around 1000-1500. This indicates that the majority of polls are conducted with smaller sample sizes. As sample size increases, the frequency significantly drops, with very few polls conducted with sample sizes larger than 5000, though there are a few outliers with sizes approaching 10,000 or more. This wide range in sample sizes might affect the precision of estimates in different polls.

### Most Frequent Pollsters

```{r}
#| warning: false
#| message: false
#| echo: false
# Get the top 10 pollsters by frequency along with their average pollscore and numeric grade
top_pollsters <- analysis_data %>%
  group_by(pollster) %>%           # Group by the 'pollster' variable
  summarize(
    Count = n(),                   # Count the number of occurrences
    Average_Pollscore = round(mean(pollscore, na.rm = TRUE), 2),  # Average pollscore
    Average_Numeric_Grade = round(mean(numeric_grade, na.rm = TRUE), 2),  # Average numeric grade
    .groups = 'drop'               # Drop grouping structure for cleaner output
  ) %>%
  arrange(desc(Count)) %>%         # Arrange in descending order of count
  slice_head(n = 10)                # Select the top 10 pollsters

# Rename the columns to remove underscores and capitalize 'Pollster'
colnames(top_pollsters) <- c("Pollster", "Count", "Average Pollscore", "Average Numeric Grade")

kable(top_pollsters, format = "markdown", caption = "Top 10 Pollsters by Frequency")

This table lists the top 10 pollsters based on the frequency of polls they conducted. Morning Consult leads with 235 polls, followed by Siena/NYT and Redfield & Wilton Strategies with 94 and 88 polls, respectively. The table also shows each pollster's average poll score and average numeric grade. Most pollsters have negative poll scores, indicating a lower perceived reliability, except for Redfield & Wilton Strategies. However, the numeric grades vary, with Siena/NYT, YouGov, and Emerson receiving relatively high grades around 3, while others like TIPP and Redfield & Wilton Strategies are rated slightly lower.

# Forcasting Election Outcome through Pooling Polls

## Forecasting Approach

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-mapinterac
#| fig-cap: "Average Support for Kamala Harris in Different States estimated by Polls"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
# Filter out non-continental states (Hawaii and Alaska)
us_states_filtered <- mapping_data %>% 
  filter(!NAME %in% c("Alaska", "Hawaii"))

@@

# Plot using geom_sf() for sf objects
p <- ggplot(map_data_full) +
  geom_sf(aes(fill = mean_support, text = paste("State:", str_to_title(NAME), "<br>Average Support:", round(mean_support, 2))), color = "white") +  # Capitalize state names
  scale_fill_distiller(palette = "RdBu", direction = 1, na.value = "gray", name = "Kamala's Support") +  # Reverse RdBu color gradient
  geom_text(data = state_centroids, aes(geometry = geometry, label = STUSPS), stat = "sf_coordinates", size = 2) +  # State labels
  labs(title = "Support for Kamala Harris by State", 
       caption = "States with no polling data are shown in gray") +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5),
    panel.grid = element_blank(),  # Remove grid lines
    axis.title = element_blank(),  # No axis titles for maps
    axis.text = element_blank(),   # No axis labels
    axis.ticks = element_blank()   # No axis ticks
  )

@@

$$
y_i = \alpha + \beta_1 \cdot \mathrm{pollster}_i + \beta_2 \cdot \mathrm{sample\_size}_i + \beta_3 \cdot \mathrm{recency}_i +  \beta_4 \cdot \mathrm{state}_i + \epsilon_i
$$

@@

```{r}
#| warning: false
#| message: false
#| echo: false
# Load the models from RDS files
model_1 <- readRDS(here("models/model_1.rds"))
model_2 <- readRDS(here("models/model_2.rds"))
model_3 <- readRDS(here("models/model_3.rds"))

@@

```{r}
#| warning: false
#| message: false
#| echo: false

# Create a data frame for AIC and BIC comparison
aic_bic_table <- data.frame(
  Model = c("Model 1", "Model 2", "Model 3"),
  AIC = c(AIC(model_1), AIC(model_2), AIC(model_3)),
  BIC = c(BIC(model_1), BIC(model_2), BIC(model_3))
)

@@

The table below shows the model output, where only a few states and pollsters are displayed to keep the output concise, as the full model includes many variables. We included "State California," "State Texas," "Pollster Redfield & Wilton Strategies," and "Pollster Echelon Insights" to provide examples of how different states and pollsters influence support for Kamala Harris.

The variable "Sample Size" has a positive coefficient, suggesting that polls with larger sample sizes are associated with slightly higher support percentages. "Recency" has a negative and highly significant coefficient, indicating that more recent polls tend to show lower support levels. Additionally, certain states like California and Texas show significant effects on the percentage of support, with California showing a notable increase. Similarly, different pollsters also display varying biases, as seen with the coefficients for "Pollster Redfield & Wilton Strategies" and "Pollster Echelon Insights." The model shows strong goodness-of-fit, with an $R^2$ of 0.731, indicating that 73.1% of the variability in support can be explained by the included variables.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
# Load necessary package
library(stargazer)

# Use stargazer to display only the specified variables and custom labels
stargazer(model_3, 
          type = "text",  # Can be "text", "html", or "latex"
          covariate.labels = c("Sample Size", "Recency", "State California", "State Texas",
                               "Pollster Redfield & Wilton Strategies", "Pollster Echelon Insights"),  # Renaming the variables
          keep = c("sample_size", "recency", "stateCalifornia", "stateTexas", 
                   "pollsterRedfield & Wilton Strategies", "pollsterEchelon Insights"),  # Keep only these variables
          omit.stat = c("f", "ser"),  # Optionally omit F-statistics or other GOF stats
          star.cutoffs = c(0.05, 0.01, 0.001),  # Custom significance stars
          single.row = TRUE)  # Display coefficients on one row for readability

# Prediction

@@

# Create a new dataset called 'predict_data' with predicted values and weights
predict_data <- analysis_data %>%
  # Add the predicted values (fitted values from model_3)
  mutate(fitted_values = fitted(model_3),
         # Create weights based on numeric grade
         weight = numeric_grade / sum(numeric_grade))

# Calculate the weighted fitted values for Kamala Harris support
weighted_support <- sum(predict_data$fitted_values * predict_data$weight)

@@

### Prediction

To predict Kamala Harris' overall support, we used a weighted average approach based on the quality of each poll. The weights are calculated using each poll's `numeric_grade`, which reflects the reliability and transparency of the polling methodology.

We define the weight for each pollster $w_i$ as follows:

$$
w_i = \frac{\mathrm{numeric\_grade}_i}{\sum_{i=1}^{n} \mathrm{numeric\_grade}_i}
$$

where:

-   $w_i$​ represents the weight assigned to poll i,

-   $numericgrade_i$ is the numeric grade of poll i, and

-   $n$ is the total number of polls used in the analysis.

Using these weights, the overall weighted prediction of Kamala Harris' support is calculated by summing the weighted predicted values from our regression model:

$$
\text{Overall Weighted Support} = \sum_{i=1}^{n} w_i \cdot \hat{y}_i
$$

-   $\hat{y}_i$​ is the predicted percentage of support for Kamala Harris from poll i.

Applying this approach, our model predicts Kamala Harris' overall support to be **47.78%**. This prediction indicates that, after adjusting for biases in the polls, Harris' support is slightly below the 50% threshold. The weighted approach accounts for the differences in poll reliability and thus provides a more accurate estimate than using raw averages of the polls.

This result suggests that Kamala Harris is facing some challenges in gaining majority support based on the current polling data. However, the model reflects the weighted average from multiple sources, smoothing out individual poll biases to offer a comprehensive view of her support landscape.

@@

In this paper, we set out to predict Kamala Harris' support using a polls-of-polls approach. By aggregating multiple polls, we aimed to smooth out the inherent biases present in individual surveys and create a more accurate and reliable forecast. Our analysis was driven by a linear regression model that used key predictors, such as pollster, sample size, state, and recency of the polls. After obtaining predicted values from the model, we applied a weighting scheme based on the numeric grade of each pollster, reflecting the quality and reliability of the poll. By assigning higher weights to more reliable pollsters, we generated a final prediction for Kamala Harris' overall support, accounting for variations across different states and polling organizations.

One key insight from our analysis is the significance of poll recency. The negative and highly significant coefficient for recency indicates that **older** polls show lower support for Kamala Harris, while more recent polls tend to show higher support. This suggests that her popularity may be increasing over time, or that certain factors have shifted voter sentiment in her favor in more recent months. Inncorporating recency into the model also greatly improved its overall performance. Adding recency as a predictor significantly increased the model's explanatory power, raising the R² value and lowering both AIC and BIC scores compared to models that excluded it. This indicates that accounting for the timing of polls is essential to accurately predicting voter sentiment, as public opinion is highly dynamic and evolves rapidly in response to events. Including recency strengthens the model's ability to reflect these temporal shifts, leading to more reliable forecasts.

Our analysis also highlights the variability in support for Kamala Harris across different states and pollsters. For example, certain states like California and Texas exhibit distinct effects, with California significantly boosting Harris’ predicted support. Additionally, different pollsters show varying levels of bias, as seen with Redfield & Wilton Strategies and Echelon Insights, which have divergent effects on support levels. This underscores the geographic and methodological complexities in predicting election outcomes, demonstrating that voter preferences are not homogenous across regions or polling firms.

Despite the strengths of the polls-of-polls methodology, there are several limitations to our approach. First, our model assumes that the relationship between the predictors (pollster, sample size, state, recency) and support for Kamala Harris is linear, which may not always be the case. Non-linear trends or interactions between variables might exist that were not captured by the model. Additionally, while we weighted polls based on their numeric grade, this metric might not fully reflect the true accuracy or bias of each pollster. Moreover, we only included polls conducted after Harris' official candidacy announcement, potentially omitting relevant data from earlier in the election cycle that could provide a fuller picture.

Future research could delve into more sophisticated methods to capture non-linear relationships and interactions between variables. For instance, incorporating machine learning algorithms like random forests or neural networks could allow for more flexible modeling of polling data. Another area of improvement could be refining the pollster weighting mechanism by integrating other factors, such as the historical performance of the pollster or specific characteristics of the electorate surveyed. Additionally, conducting more in-depth analyses of key battleground states could reveal more granular insights into voter behavior, especially in regions where small shifts in support could have outsized impacts on election outcomes.

In conclusion, while our model provides valuable predictions of Kamala Harris' support, there is always room to enhance the predictive accuracy by refining methodologies and incorporating new data sources. The evolving nature of elections demands continuous adjustment of models to reflect changes in public opinion, candidate strategies, and electoral dynamics.

@@

@@
